A holomorphic approach to branes in twisted~$M$-theory

### 2022-09-21 fivebranes/index.tex
prop 3.2

\begin{prop}
Up to completion, the cohomology $H^{\bu}(\Gamma(\cA_{\mathring M}^{\bu}(\cL)), \thfD)$ is a direct sum of the cohomology on flat space $H^{\bu}(\gamma(\cA)$
\end{prop}

>>>>

\surya{sloppy about hypercohomology}
\begin{prop}
  Up to completion, the cohomology $H^{\bu}(\Gamma(\cA_{\mathring M}^{\bu}(L)), \thfd)$ is a direct sum of the cohomology on flat space $H^{\bu}(\Gamma(\cA)(L), \thfd)$ with the complex

  \beeqn
  \begin{tikzcd}[row sep = 1 ex]
    + & - \\ \hline
w_1^{-1} w_2^{-1} \CC[w_1^{-1}, w_2^{-1}][z_1,z_2,z_3] \{\partial_{w_i}\}  \ar[r, dotted, "D_{\Omega}"] & w_1^{-1} w_2^{-1} \CC[w_1^{-1}, w_2^{-1}] [z_1,z_2,z_3] \\
w_1^{-1} w_2^{-1} \CC[w_1^{-1}, w_2^{-1}] [z_1,z_2,z_3] \{\del_{z_i}\} \ar[ur, dotted, "D_{\Omega}"'] \\
w_1^{-1} w_2^{-1} \CC[w_1^{-1}, w_2^{-1}] [z_1,z_2,z_3] \ar[r, dotted, "D"] \ar[dr, dotted, "D"'] & w_1^{-1} w_2^{-1} \CC[w_1^{-1}, w_2^{-1}][z_1,z_2,z_3] \{\d z_i\} \\ & w_1^{-1} w_2^{-1} \CC[w_1^{-1}, w_2^{-1}][z_1,z_2,z_3] \{\d w_i\} .
\end{tikzcd}
\eeqn
\end{prop}
